Stellar Migration and Chemical Enrichment in the Milky Way Disc: A Hybrid Model

### 2021-08-04 chemev/MWbimodality/paper/draft2/normalize_sfh.tex
migration paper referee response

\documentclass[fleqn, usenatbib]{mnras} 
\usepackage{newtxtext, newtxmath} 	% Required for MNRAS 
\usepackage[T1]{fontenc} 
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{multicol}
\usepackage{bm}
\usepackage{pdflscape}
\usepackage{natbib}
\usepackage[section]{placeins}
\usepackage{lipsum}
\usepackage{etoolbox} 
\usepackage{tabularx} 
\usepackage{xcolor} 
\usepackage[toc, page]{appendix} 
% \hypersetup{draft} 
% \linespread{1.8} 
\hypersetup{ 
	colorlinks		= true, 
	urlcolor 		= blue, 
	linkcolor 		= blue, 
	citecolor 		= blue 
}

\newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
\newcommand{\refp}[1]{(\ref{#1})} 
\newcommand{\msun}{\ensuremath{\text{M}_\odot}} 
\newcommand{\persqkpc}{\ensuremath{\text{kpc}^{-2}}} 
\providecommand{\noopsort}[1]{} 
\graphicspath{ {../plots/} }

\interfootnotelinepenalty = 10000 
\defcitealias{Kroupa2001}{Kroupa} 
\defcitealias{Salpeter1955}{Salpeter}

\title[Stellar Migration and Chemical Enrichment]{Stellar Migration and 
Chemical Enrichment in the Milky Way Disc: A Hybrid Model}

\author[J.W. Johnson et al.]{
	James W. Johnson,$^{1}$\thanks{Contanct e-mail: \href{mailto:
	johnson.7419@osu.edu}{johnson.7419@osu.edu}} 
	David H. Weinberg,$^{1, 2, 3}$ 
	Fiorenzo Vincenzo,$^{2}$ 
	Jonathan C. Bird,$^{4}$ 
	\newauthor 
	Sarah R. Loebman,$^{5}$ 
	Alyson Brooks,$^{6}$ 
	Thomas R. Quinn,$^{7}$ 
	Charlotte R. Christensen,$^{8}$ 
	\newauthor 
	et al.?
	\\
	$^{1}$ Department of Astronomy, The Ohio State University, 
	140 W. 18th Ave., Columbus, OH, 43210, USA 
	\\ 
	$^{2}$ Center for Cosmology and Astroparticle Physics (CCAPP), 
	The Ohio State University, 191 W. Woodruff Ave, Columbus, OH, 43210, USA 
	\\ 
	$^{3}$ Institute for Advanced Study, 1 Einstein Dr., Princeton, NJ, 08540, 
	USA 
	\\ 
	$^{4}$ Department of Physics \& Astronomy, Vanderbilt University, 
	2301 Vanderbilt Place, Nashville, TN, 37235, USA 
	\\ 
	$^{5}$ Department of Physics, University of California Merced, 
	5200 North Lake Rd., Merced, CA, 95343, USA 
	\\ 
	$^{6}$ Department of Physics \& Astronomy, Rutgers University, 136 
	Frelinghuysen Rd, Piscataway, NJ, 08854, USA 
	\\ 
	$^{7}$ Department of Astronomy, University of Washinton, Box 351580, 
	Seattle, WA, 98195, USA 
	\\ 
	$^{8}$ Department of Physics, Grinnell College, 1116 8th Ave., Grinnell, 
	IA, 50112, USA 
}

\date{Accepted XXX; Received YYY; in original form ZZZ} 
\pubyear{2020}

\begin{document} 
\label{firstpage} 
\pagerange{\pageref{firstpage}--\pageref{lastpage}} 
\maketitle

\begin{abstract} 
We investigate the impact of stellar migration on galactic chemical evolution 
models, considering a handful of assumptions for the star formation history 
and time-dependence of radial migration based on a zoom-in, hydrodynamical 
simulation of galaxy evolution. When stars migrate with a smooth, continuous 
time dependence, the type Ia supernova rate exhibits significant variability in 
our models. We demonstrate that this is a means with which young, super-solar 
[$\alpha$/Fe] in the solar neighbourhood can arise naturally out of inside-out 
Galaxy growth with stellar migration. We find 
that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
formation history, while the age-[$\alpha$/H] and age-[Fe/H] relations are 
well-fit by a late starburst model; no one model investigated here fits both 
simultaneously. Our model successfully reproduces the broad nature of the 
[$\alpha$/Fe] distribution at fixed [Fe/H] in a given Galactic region; however, 
an overprediction of the frequency of intermediate [$\alpha$/Fe] stars prevents 
it from explaining the observed results in detail. This suggests 
that inside-out galaxy growth combined with stellar migration, even with a late 
starburst, is not conducive to forming the infamous bimodality as it is 
observed. We postulate that more dramatic evolutionary scenarios (e.g. a 
two-infall model) may be necessary to describe the observed results. In 
conducting this analysis, we developed and made use of newly released features 
in the \texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}) 
which are built to handle these models under a wide variety of 
assumptions. \texttt{VICE} is publicly available 
at~\url{https://pypi.org/project/vice}. 
\end{abstract}

\begin{keywords} 
methods: numerical -- galaxies: abundances, evolution, star formation, stellar 
content 
\end{keywords}

\section{Introduction} 
\label{sec:intro} 
The orbits of stars are not unchanging. While it has been known for some time 
that stars undergo radial migration (e.g.~\citealp*{Wielen1996}; 
\citealp{Roskar2008a,Loebman2011,Minchev2012}), the true impact of this process 
on galactic chemical evolution (GCE) remains under debate. By mixing stellar 
populations which formed in Galactic regions with significantly different 
enrichment histories, in principle the impact could be considerable. While some 
authors argue that radial migration has only a small impact on GCE 
(e.g.~\citealp*{Kubryk2013};~\citealp{Khoperskov2021}), there are others who 
argue the contrary (e.g.~\citealp{Schoenrich2009};~\citealp*{Sharma2020}). 
Aside from the chemodynamical simulations involving N-body integrations 
\citep[e.g.][]{Kubryk2013, Vincenzo2020, Khoperskov2021}, there are to date 
only a handful of GCE models that take this effect into account (e.g. 
\citealp{Matteucci1989, Schoenrich2009};~\citealp*{Minchev2013}; 
\citealp{Sharma2020}). These studies treat the Milky Way as a series of 
concentric annuli, each described by a conventional one-zone GCE model with 
parameters that change from annulus to annulus. In the resultant ``multi-zone'' 
model, stars and gas can migrate between zones under some prescription to 
account for time-dependent mixing processes. We retain such methodology in this 
paper, allowing star particles from a hydrodynamical simulation ran from 
cosmological initial conditions to inform our implemented mixing process; 
\citet{Minchev2013} employ a similar technique. With parameters tuned to 
reproduce certain observed results (e.g. abundance and surface density 
gradients), we can then assess the model predictions to address the following 
question: when combining simple, conventional assumptions about the star 
formation and dynamical histories of the Milky Way, what observed results can 
be replicated? In the present paper, we focus on the following observables: 
metallicity distributions functions (MDFs) and abundance gradients, the 
[$\alpha$/Fe] bimodality, the age-metallicity relation (AMR), and the young, 
$\alpha$-rich population. 
Stars in the inner regions of the Milky Way tend to be more metal-rich than 
those found in the outskirts~\citep{Nordstroem2004b, Daflon2009, 
Frinchaboy2013, Hayden2014}, with slight variations in quantitative results 
based on what type of stars are considered and what metallicity tracers are 
analysed. Such behavior is also seen in the gas-phase gradients of 
low-redshift spirals (see, e.g., the results from the CHAOS project using HII 
regions;~\citealp{Berg2015, Berg2020}). Using the 12th data release of the 
Apache Point Observatory Galaxy Evolution Experiment (APOGEE), 
\citet{Hayden2015} demonstrate that the observed MDF has a metal-rich mode and 
is skew-negative in the inner galaxy (and conversely, metal-poor and 
skew-positive in the outer galaxy). These variations in the skewness of the 
distributions with Galactocentric radius are usually attribute to the migration 
of metal-rich (metal-poor) stars from smaller (larger) orbital radii. Similar 
arguments are used by~\citet{Sellwood2002} to interpret the results of 
\citet{Edvardsson1993} on scatter in the age-metallicity relation observed in 
the solar neighbourhood. 
Abundance gradients have been the focus of many studies and are quantified 
rather extensively, but their origin is somewhat up for debate. Applying the 
analytic models of~\citet*{Weinberg2017}, one could argue that the gradient 
arises out of variations in the local gas-phase equilibrium abundance as a 
function of Galactocentric radius. For $\alpha$-elements, the equilibrium 
abundance is determined to first order by their yield and the efficiency of 
outflows in removing metals from the star forming reservoir. With a stronger 
gravitational potential in the inner regions of the Galaxy, one might 
reasonably expect outflows to be weaker there, thereby increasing the 
equilibrium abundance.~\citet{Nidever2014} used such an approach to reproduce 
the width of the [Fe/H] distribution for low-$\alpha$ sequence stars in 
APOGEE. However, recent chemical evolution models have successfully replicated 
the gradient with no outflowing winds at all~\citep[e.g.][]{Minchev2013, 
Spitoni2019a}. This is based on arguments from~\citet{Melioli2008, Melioli2009}, 
\citet*{Spitoni2008}, and~\citet{Spitoni2009} who studied Galactic fountains 
using hydrodynamical simulations and numerical models, finding that ejected 
metals tend to reaccrete to a Galactocentric radius similar to where they 
originated. With this result, some authors argue that such outflows do not 
significantly alter the chemical evolution of a Galactic disc, and that instead 
the gradient arises from the higher normalization of the star formation history 
in the inner Galaxy. 
Like radial abundance gradients, the reality of the infamous [$\alpha$/Fe] 
dichotomy is well established (in Gaia-ESO:~\citealp{Recio-Blanco2014, 
Rojas-Arriagada2017}; in APOGEE:~\citealp{Nidever2014, Hayden2015, 
Weinberg2019}), but its origin is a topic of intense debate. In general, stars 
in the Milky Way tend to fall in one of two populations - the roughly solar 
[Fe/H], solar [$\alpha$/Fe] stars commonly referred to as the low-$\alpha$ 
sequence, and the high-$\alpha$ sequence made up of sub-solar [Fe/H], 
super-solar [$\alpha$/Fe] stars. Recently explored with more current data by 
\citet{Sharma2020}, the notion that it could in principle arise out of radial 
migration traces back to~\citet{Schoenrich2009}. Applying the analytic models 
of~\citet{Weinberg2017}, an alternative pathway to such abundance patterns is 
by an increase in the strength of outflows at late times. Such an evolutionary 
model would predict a decrease in the equilibrium abundance, forming stars 
along the low-$\alpha$ sequence. This scenario has not yet been explored in 
combination with radial migration. 
Other authors argue that more dramatic evolutionary events are necessary to 
explain the observed results, such as the two-infall model 
(\citealp*{Chiappini1997, Chiappini2001};~\citealp{Romano2010, Grisoni2017, 
Noguchi2018, Palla2020, Spitoni2016, Spitoni2018}). 
In these models, the high-$\alpha$ sequence forms during the Galaxy's initial 
collapse before feedback processes shut off star formation and expel gas into 
the Galactic halo. Then, this material can cool and reaccrete along with 
additional, metal-poor gas from the intergalactic medium, producing a second 
episode of star formation. The dilution associated with the second accretion 
event lowers the gas-phase Fe abundance at fixed [$\alpha$/Fe], forming stars 
along the low-$\alpha$ sequence.~\citet{Spitoni2019a, Spitoni2020} demonstrated 
using the APOKASC sample~\citep{Pinsonneault2014, SilvaAguirre2018} that such 
models can explain the abundances observed in the solar annulus. Although 
\citet{Spitoni2021} recently extended this model to Galactic regions beyond 
the solar annulus, their model did not account for the mixing of stellar 
populations between regions. Though they invoke~\citet{Kubryk2013} and 
\citet{Khoperskov2021} as arguments that it shouldn't impact their results, 
this nonetheless means that two-infall models have not yet been explored in 
combination with a treatment for stellar migration. 
Recent cosmological zoom-in simulations have found results qualitatively 
similar to the arguments of~\citet{Spitoni2019a, Spitoni2020, Spitoni2021}. 
Using the Auriga simulation suite~\citep{Grand2017},~\citet{Grand2018} 
demonstrate that an early, accretion induced starburst can populate the 
high-$\alpha$ sequence, followed by low-level, sustained star formation on the 
low-$\alpha$ sequence. In this pathway, there is either a rapid transition 
between the two phases, ensuring the chemical space between the sequences is 
relatively unpopulated, or low-metallicity gas accretion dilutes the star 
forming reservoir at fixed [$\alpha$/Fe], populating the low [Fe/H], low 
[$\alpha$/Fe] portion of the low-$\alpha$ sequence.~\citet{Buck2020b} finds 
the dilution scenario in the NIHAO simulation suite as well~\citep{Wang2015, 
Buck2020a}. Although the~\citet{Spitoni2021} model did not implement mixing of 
stellar populations, these studies using hydrodynamical simulations would 
suggest pathways qualitatively similar to their two-infall model. 
Contrary to this scenario,~\citet{Clarke2019} demonstrate that star formation 
proceeded in clumps in an SPH simulation using GASOLINE~\citep*{Wadsley2017}. 
These clumps self-enrich, forming stars on the high-$\alpha$ sequence due to 
the perturbed ratio of core collapse to type Ia supernova rates within the 
star forming regions. The more spatially extended, smooth star formation 
populates the low-$\alpha$ sequence. Suffice it to say that there are no 
shortage of models which reproduce the dichotomy, but only those done with 
hydrodynamical simulations and a handful of others 
\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020} have taken into account 
stellar migration. 
Besides abundance gradients and the [$\alpha$/Fe] dichotomy, another 
observable of interest in this paper is the age-metallicity relation (AMR): the 
correlation between stellar ages and metallicities. The observed AMR in the 
solar neighbourhood is known to exhibit considerable intrinsic scatter 
\citep{Edvardsson1993}; this is usually attributed to radial migration of 
metal-rich (metal-poor) stars from smaller (larger) Galactocentric radii 
\citep{Sellwood2002, Haywood2008, Roskar2008b, Schoenrich2009}. 
In the solar neighbourhood,~\citet{Feuillet2018} reveal that super-solar 
metallicity stars are statistically older than solar metallicity stars (see 
their Fig. 3). This contrasts with the predictions of simple one-zone models of 
GCE where enrichment proceeds alongside star formation, yielding a monotonic 
AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. Although one-zone models of 
starbursts can predict a non-monotonic AMR due to the effect of dilution 
\citep{Johnson2020}, by construction they do not predict multiple abundances at 
fixed age as~\citet{Feuillet2018} reports. Using the~\citet{Weinberg2017} 
analytic models,~\citet{Feuillet2018} argues that this is a consequence of 
radial migration. For a smooth star formation history, the youngest stars at a 
given radius will have compositions reflective of the local equilibrium 
abundance; only stars born at different radii will have different compositions, 
and only the old ones will have had time to migration to the solar annulus. 
While the presence of old-metal rich stars in the solar annulus is peculiar 
because they are at odds with one-zone models of chemical evolution, the 
presence of young, $\alpha$-rich stars is interesting for the same reason. 
For a smooth star formation history, the delayed nature of type Ia supernovae 
and their Fe production cause [$\alpha$/Fe] to decrease with time, predicting 
an age-[$\alpha$/Fe] relation that should increase monotonically with stellar 
age. However, these~$\sim$few Gyr old stars with [$\alpha$/Fe]~$\approx$~+0.1 - 
0.2 stars have been found using stellar ages estimated from carbon-to-nitrogen 
ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
Feuillet2019}, and with the asterosesmic ages of the original APOKASC catalog 
\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
\citet{SilvaAguirre2018} demonstrate that these stars have kinematics similar 
to the rest of the high-$\alpha$ population, postulating that they may be 
the consequence of stellar mergers or mass transfer events, making truly old 
stars simply appear younger. In a sample of 51 young, $\alpha$-enhanced red 
giant stars,~\citet{Hekker2019} conclude that a portion of these stars have 
carbon-to-nitrogen ratios consistent with mass transfer events, but that this 
cannot account for the entire population. This suggests that the remaining 
stars are either truly young or the result of mergers on the main sequence. 
If not, then a theoretical explanation for the origin of these stars remains 
a mystery. 
Alternatively, a recent starburst event could have produced these stars. 
\citet{Mor2019} infer a factor of~$\sim$2 enhancement in the star formation 
history (SFH) of the Milky Way~$\sim$2 Gyr ago by comparing population 
synthesis models to observed stellar luminosity functions and colour-magnitude 
diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach similar 
conclusions by modeling the white dwarf luminosity function in the solar 
neighbourhood with Gaia parallaxes. Motivated by these results, 
\citet{Johnson2020} demonstrate using one-zone chemical evolution models that 
a recent starburst of this nature can produce similarly young,~$\alpha$-rich 
stars. However, the caveat to this interpretation is that the starburst must be 
sufficiently localized such that the resultant stellar populations remain 
outliers from an otherwise monotonically increasing age-[$\alpha$/Fe] relation. 
The impact of such evolutionary histories combined with stellar migration is, 
to our knowledge, yet unexplored in the literature. A viable model for the 
detailed enrichment history of the Milky Way would simultaneously explain all 
of these observed results and their variations between Galactic regions, while 
also taking into account effects like mixing and observational systematics. On 
top of this, it must self-consistently calculcate enrichment rates from adopted 
nucleosynthetic yields and the SFH. In this paper, we aim to 
assess the extent to which conventional assumptions about the evolutionary 
history of the Milky Way can account for these results, entertaining a 
handful of assumptions describing the SFH and time-dependence of stellar 
radial migration. 
Motivated by the general result that galaxies grow in radius with time 
(i.e. ``inside-out'' growth;~\citealp{Bird2013}), our base-line model has a 
star formation history (SFH) whose e-folding timescales grow with 
Galactocentric radius. Based on the findings of~\citet{Mor2019} and 
\citet{Isern2019}, we also construct models in which a late starburst is 
imposed atop the inside-out SFH. In one model, this starburst occurs in all 
annuli, and in another, loosely informed by the findings of 
\citet{Vincenzo2020} suggesting such a radial dependence to accretion, it 
occurs only at~$\geq$6 kpc. We also construct a model in which the SFH is 
constant at a given Galactocentric radius; these models are interesting from a 
theoretical perspective in that they quantify the impact of stellar migration 
without the effects of a time-dependent SFH.

\section{Methods} 
\label{sec:methods} 
To fulfill the goals of this paper, we develop and make use of newly released 
features within the~\texttt{Versatile Integrator for Chemical Evolution} 
(\texttt{VICE};~\citealp{Johnson2020}). These features are designed to handle 
models such as these with a wide range of flexibility. We reserve a description 
of~\texttt{VICE}'s migration algorithm and our simulation parameters for~\S 
\ref{sec:methods:migration}, first describing our sample of star particles from 
the hydrodynamical simulation. 
\par 
Although we make use of a hydrodynamical 
simulation to drive stellar migration, we do~\textit{not} make use of its SFH. 
While our study employs similar techniques as~\citet{Minchev2013}, our differs 
in this subtle aspect. An alternative to modeling radial migration based on a 
hydrodynamical simulation is to invoke dynamical arguments; 
\citet{Schoenrich2009} and~\citet{Sharma2020} take such an approach. This 
method, however, introduces free parameters which then require fitting to 
data. An advantage of our technique is that there are no free parameters 
introduced to the model; furthermore, it's unclear the extent to which the fit 
biases the model into agreement with parts of the data not involved in the 
fitting process. The dynamical history of a hydrodynamical simulation is also 
motivated by first principles in that it models gravitational interactions via 
an N-body integration. The primary disadvantage of this approach is a 
consequence of the lack of free parameters - the model is rigid, and we cannot 
explore slight variations. However, in principle one could compare the 
predictions made by our chemical evolution models when ran using different 
hydrodynamical simulations. We emphasize that a hydrodynamical simulation 
\textit{only} informs the mixing processes in our models, and there is no 
N-body integration involved in our models aside from that which was used to run 
the hydrodynamical simulation in the first place.

\subsection{The Hydrodynamical Simulation} 
\label{sec:methods:h277} 
In this paper we make use of star particles from the~\texttt{h277} simulation 
\citep{Christensen2012, Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. 
Recently employed to study the stellar age-velocity relationship, a synopsis of 
its detailed simulation parameters and cosmological model can found in~\S 2 of 
\citet{Bird2020}. We do not include any discussion of these details here, 
instead focusing on how we vet the sample of star particles for use in our 
chemical evolution models. 
It is of particular important to have accurately measured formation radii for 
each star particle that we use in our analysis.~\texttt{h277} did not record 
the exact birth radius of each star particle; however, each star particle does 
have an accurate age at each snapshot. Since stellar orbits are unlikely to 
change significantly in an adequately short time interval, the radii of 
sufficiently young stars in their first snapshot are reasonable approximations 
of their birth radii. We therefore restrict our sample to those with an age at 
first snapshot of~$\leq$~150 Myr, and adopt their Galactocentric radius at that 
time as their birth radius. We have also conducted this analysis with a maximum 
age at first snapshot of 50 Myr, and found similar results, suggesting that 
these time intervals are short enough to not impact our conclusions. In 
practice, we find that 150 Myr also provides with an adequately large number of 
star particles to sample from. Of the star particles that remain after imposing 
this cut, the oldest one is 12.26 Gyr old at the present day. Our model can 
only apply on timescales as long as or shorter than the full range of ages of 
the sample of star particles; we therefore subtract 1.5 Gyr from the formation 
times of all star particles, allowing~$T$~= 0 in our models to correspond to 
$T$~= 1.5 Gyr in~\texttt{h277}. As a consequence, our disc models trace the 
chemical evolution of the Galaxy out to a lookback time of~$\sim$12.2 Gyr, or a 
redshift of~$z \approx$~3, placing the onset of star formation at that time. 
We further restrict our sample of star particles to only those with both 
formation and final radii of~$R_\text{gal} \leq$~20 kpc, and to have formed 
within~$\left|z\right|\leq$~3 kpc of the disc midplane. These criteria ensure 
that we're only using star particles which formed in-situ. While it's possible 
that some star particles formed in a dwarf galaxy as it was infalling, a 
scenario which would satisfy these requirements, these star particles are few 
in number, and are only relevant at large~$R_\text{gal}$ and high ages - a 
region of parameter space where few stars form anyway. 
Based on a kinematic decomposition performed on the present-day phase space 
distribution of the~\texttt{h277} star particles, we include all those with 
bulge, pseudobulge, and disc-like kinematics, excluding halo stars. While we're 
not modeling the evolution of the bulge here, these star particles are 
overwhelmingly located at~$R_\text{gal}\leq$~3 kpc at the present day anyway; 
here we're much more interersted in~$R_\text{gal}\geq$~3 kpc since we're 
modeling the evolution of the disc. These cuts yield a sample of 3,000,556 star 
particles from~\texttt{h277}. 
\texttt{h277} had a transient bar during its evolution, but does not have one 
at~$z$ = 0 ({\color{red} citation?}). This is a noteworthy difference between 
our model and that of~\citet{Minchev2013}, and by extension the 
\citet*{Minchev2014} and~\citet{Minchev2017} studies which use it as well, 
because they selected a hydrodynamical simulation of a galaxy specifically so 
that it would have a strong bar at~$z$ = 0; the transient bar in~\texttt{h277} 
was not strong. This could mean that the dynamical 
history of our model Galaxy does not reflect that of~\citet{Minchev2013} and 
perhaps the Milky Way itself. However, the difference is likely within the 
uncertainties of the current understanding of the Milky Way's dynamical 
history. Although an investigation on the impact of bar evolution on stellar 
migration and thus chemical evolution is outside the scope of this paper, it is 
an interesting question which can be probed by simply swapping the 
\texttt{h277} data within~\texttt{VICE} for another simulation, then rerunning 
our numerical models and comparing the results.

% fig 1 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{decomposition.pdf} 
\caption{Radial distributions of our star particles from 
\texttt{h277}. In the top row, we show distributions of~\textit{final} radius 
in bins of birth radius and age, and in the bottom row, we show distributions 
of~\textit{birth} radius in bins of final radius and age. Each bin in 
Galactocentric radius is shown in its own panel, denoted in text at the top of 
each panel and by vertical black dashed lines. We colour-code the distributions 
according to the age of the star particles, denoted by the legend in the upper 
left panel. We smooth all distributions with a box-car width of 0.5 kpc to 
improve clarity. We omit the distributions for 8 - 10 Gyr old stars born in the 
9 - 11 and 11 - 13 kpc bins due to an insufficient number of star particles 
with which to calculate the distribution. } 
\label{fig:h277_decomposition} 
\end{figure*}

In the top row of Fig.~\ref{fig:h277_decomposition}, we plot the distributions 
of final radius in bins of birth radius and age for our sample of star 
particles. Conversely, the bottom rows distributions of birth radii in bins of 
final radius and age. Focusing on the top row of panels, we note that for star 
particles born at any radius and time, the distribution of final radius is 
still peaked near the birth radius, but moves slightly inward with increasing 
age. The tails of the distributions toward larger~$R_\text{gal}$ are nearly 
age-independent, while the tails toward smaller~$R_\text{gal}$ are not. This 
suggests that radial migration inward and outward occur on different timescales 
in~\texttt{h277}, specifically that inward migration is slower than outward 
migration. By extension, this suggests that the two may be tied to different 
physical processes. In a cosmological simulation,~\citet{Roskar2008a} 
demonstrate that resonant scattering at corotation causes stars to move 
outward and gas to move inward. It's possible that stellar migration inward has 
different origins. 
Focusing on the bottom row of panels in Fig.~\ref{fig:h277_decomposition}, we 
note that the mode of the birth radius distributions show a stronger dependence 
on age than the mode of the final radius distributions. At any Galactocentric 
radius at the present day, the youngest stars are overwhelmingly born at 
comparable radii, while the oldest stars are overwhelmingly born at smaller 
radii. This is most noticeable in at large~$R_\text{gal}$. The differences 
between the two can be understood by considering the steep nature of the radial 
gradient in stellar surface density. Take for example the 8 - 10 Gyr age bin in 
both~$R_\text{Birth}$ = 5 - 7 kpc and~$R_\text{Final}$ = 11 - 13 kpc bins (i.e. 
the red curves in the top-left and bottom-right panels). For these old stars 
born at 5 - 7 kpc, 11 - 13 kpc is far down the tail of the~$R_\text{Final}$ 
distribution, and yet 5 - 7 kpc is the mode~$R_\text{Birth}$ of all old stars 
presently at these radii. This implies that even though a plurality of 8 - 10 
Gyr old stars with~$R_\text{Final}$ = 11 - 13 kpc were born at 5 - 7 kpc, they 
account for only a small fraction of the stars with similar birth radii. This 
is only possible if there are many more stars born at small~$R_\text{gal}$ than 
large~$R_\text{gal}$, implying a stellar surface density which decreases as a 
strong function of Galactocentric radius. This is known to be the case 
\citep[e.g.][]{Bland-Hawthorn2016}. 
We also note that the top row of Fig.~\ref{fig:h277_decomposition} demonstrates 
that the number of stars which migrated inward and outward are comparable in 
\texttt{h277}. In fact, taking~$\left|\Delta R_\text{gal}\right| \geq$~500 pc 
between birth and final radii as the criterion for migration inward or outward, 
we indeed find as global percentages in our sample that 27\% migrated inward, 
29\% migrated outward, and the remaining 44\% stayed near their birth radius. 
Furthermore, these distributions contain some information on the timescales of 
radial migration. In all bins of birth radius, a good first-order estimate of 
the probability density that a star has a final radius in the same bin is 
$\sim$0.3. With bins in birth radius of 2 kpc, this suggests that only 
$\sim$60\% of stars remain in their birth radius bin by the time their~$\sim$2 
Gyr old. and the remaining~$\sim$40\% have migrated already. If the type Ia 
supernova delay-time distribution (SN Ia DTD) is a~$t^{-1.1}\approx t^{-1}$ 
power-law as suggested by observational results~\citep[e.g.][]{Maoz2012, 
Maoz2017}, then we expect similar numbers of SN Ia events to occur with delay 
times between 1 and 10 Gyr as we do between 100 Myr and 1 Gyr. With such an 
extended DTD, and the timescales for migration implied by Fig. 
\ref{fig:h277_decomposition}, its possible that SN Ia progenitors can migrate 
significant distances before exploding. Indeed, in the ASAS-SN bright SN 
catalog,~$\sim$10\% of SNe are seen at >10 kpc from their host galaxies 
\citep{Holoien2019}. While this catalog is for~\textit{all} supernovae seen by 
ASAS-SN, the majority of SN events are type Ia anyway. Based on this, it's 
reasonable to expect that the migration of nucleosynthetic may proceed 
alongside stellar migration. This effect has largely been neglected by GCE 
studies to date on the grounds that radial migration is a slow process, and 
thus the majority of nucleosynthesis should occur near a star's birth radius 
(e.g.~\citealp{Minchev2013}, and in the application of the 
\citealt{Weinberg2017} analytic models in~\citealt{Feuillet2018}). However, 
with the realization that the SN Ia duty cycle is also a slow process due to 
the long tail of the DTD, its possible that stellar migration and SN Ia occur 
on similar timescales. Therefore, we relax this assumption in the present 
paper. We discuss the application of the~\texttt{h277} star particle data to 
our model for radial migration and the time dependence thereof in the next 
section.

\subsection{Radial Migration} 
\label{sec:methods:migration} 
As in previous studies~\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020}, 
in this paper we model the Milky Way as a series of concentric annuli with a 
uniform width~$\Delta R_\text{gal}$. To run numerical simulations of these 
models, we develop and make use of~\texttt{VICE}'s~\texttt{milkyway} object, 
designed specifically for such an approach. The~\texttt{milkyway} object is a 
subclass of a more general object named~\texttt{multizone}; at its core a 
\texttt{multizone} object is an array of~\texttt{singlezone} objects, which are 
designed to handle one-zone models of GCE and were the focus of 
\citet{Johnson2020},~\texttt{VICE}'s initial release paper. The 
\texttt{multizone} object affords users full control over which zone any 
individual stellar population is in at all timesteps following its formation as 
well as the ability to move gas between any two zones with any time dependence. 
In principle this should allow for arbitrarily complex zone configurations and 
migration prescriptions. The \texttt{milkyway} object is a user-friendly 
extension of this which enforces an annular zone configuration as we take here. 
As defaults, it adopts the stellar migration model detailed in this section and 
our star formation law discussed in~\S~\ref{sec:methods:sfe}. 
As in hydrodynamical simulations, stars in~\texttt{VICE} are stand-ins for 
entire stellar populations. They're said to be in a given zone if their radius 
is between the inner and outer edges of the annulus. At all times, their 
nucleosynthetic products and returned envelopes are placed in the ISM of the 
annulus that they are in~\textit{at that time}. Where hydrodynamical and 
N-body simulations of Galaxy evolution tend to use star particles of a fixed 
mass, however,~\texttt{VICE} forms a fixed number of stellar populations per 
zone per timestep, and allows their masses to vary to account for variations 
in the star formation rate (SFR). The mass of stars formed in a given zone is 
divided evenly among the stellar populations that form in a given zone and 
timestep. 
The final radius of a stellar population is then determined based on the birth 
and final radii of star particles in a hydrodynamical simulation, for which 
we've taken~\texttt{h277} in this paper (see discussion in~\S 
\ref{sec:methods:h277}). Describing the Galaxy as a series of concentric 
annuli,~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations 
are born at the centres of each annulus. For a stellar population born at a 
time~$T$ and Galactocentric radius~$R_\text{gal}$, it first searches for star 
particles from~\texttt{h277} that formed at~$T \pm$~250 Myr and~$R_\text{gal} 
\pm$~250 pc. It then randomly selects a star particle from this subsample with 
no bias to act as an~\textit{analog}. This stellar population then assumes the 
change in orbital radius~$\Delta R_\text{gal}$ of its analog at face value, 
and moves from its birth radius to the implied final radius at~$T$ = 12.2 Gyr 
with an assumed time dependence. If no candidate analogs are found, 
\texttt{VICE} widens the search to~$T \pm$~500 Myr and~$R_\text{gal} \pm$~500 
pc. If still no analog is found, then it finds the star particle 
with the smallest difference in birth radius still within a birth time of 
$T \pm$~500 Myr, and assigns it as the analog. 
While this prescription allows stellar populations to be assigned analogs with 
significantly different birth radii, this is only an issue for small~$T$ and 
large~$R_\text{gal}$ where there are few star particles from~\texttt{h277}, 
and where few stars form in nature anyway due to the inside-out growth of 
galaxies~\citep{Bird2013}. Furthermore, due to the similarity of the histograms 
in the top row of Fig.~\ref{fig:h277_decomposition}, we expect taking 
$\Delta R_\text{gal}$ from a star particle which formed at a similar time but 
different birth radius in these instance to be accurate enough for our 
purposes. 
Our models assume that the Galaxy is vertically and azimuthally well-mixed, and 
that the radial direction is the only one in which there are significant 
differences in composition. That is, each annulus extends from the disc 
midplane at~$z$ = 0 to~$z = \pm \infty$, and whether or not a star particle is 
in a given annulus does not depend on~$z$ at all. In fact, this information is 
\textit{not} used in integrating our models with~\texttt{VICE}. Instead, we 
simply assume that each stellar population in our models are located at the 
present day~$z_\text{final}$ of its assigned analog. Furthermore, when an 
\texttt{h277} star particle is assigned as an analog, it is~\textit{not} 
thrown out of the sample of candidate analogs, in theory allowing a star 
particle to act as an analog for multiple stellar populations. This is a 
subtle difference between the~\citet{Minchev2013} model and ours; where we 
assign star particles to stellar populations for which~\texttt{VICE} then 
calculates a stellar mass and composition based on an assumed SFH, the 
\citet{Minchev2013} uses a chemical evolution model to assign compositions to 
star particles.

% fig 2 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{migration.pdf} 
\caption{A diagram illustrating how Galactocentric radius changes with time for 
two stellar populations under our migration schema: diffusion (crimson, solid), 
linear (lime, dot-dashed), post-process (black, dotted), and sudden (blue, 
dashed). Here the initial and final radii and birth times are chosen at random 
for illustrative purposes. With the initial and final Galactocentric radii of 
a stellar population, its birth time, and one of these assumptions regarding 
the time-dependence of radial migration, the Galactocentric radius at all times 
is known. } 
\label{fig:migration_schema} 
\end{figure}

>>>>

\documentclass[draft2.tex]{subfiles} 
\begin{document}

\section{Normalizing the Star Formation History} 
\label{sec:normalize_sfh}
